Transfer learning for echelle spectroscopy

### 2021-11-10 paper/paper1/ms.tex
Writing equations in the paper

\documentclass[modern]{aastex631}
\bibliographystyle{aasjournal}
\turnoffedit
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{censor}

@@

where $V(\lambda, \sigma_j, \gamma_j)$ is the normalized Voigt profile with Gaussian standard deviation $\sigma$, Lorentzian half-width $\gamma$, at line center position $\lambda_c$, for the $j^{th}$ spectral line.  The amplitude $a$ is equal to the area under the curve of the line.

The model evaluated with its coarse initial values would have terrible performance: it would only vaguely resemble the synthetic spectral model, with up to $\pm 50\%$ undulations from the inexact assignment of widths,lineshapes, and amplitudes.  Instead, we tune the parameters of the model, starting from these coarse initial values.  This model has $N_{\mathrm{lines}}\times 3$ free parameters, where the center wavelength is held fixed and the amplitude, width, and lineshape are allowed to vary.

As seen in Figure XX, the number of lines can exceed $XX$ depending on the

>>>>

\documentclass[modern]{aastex631}
\bibliographystyle{aasjournal}
\turnoffedit
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{censor}
\usepackage{mathtools}

@@

where $V(\lambda, \sigma_j, \gamma_j)$ is the normalized Voigt profile with Gaussian standard deviation $\sigma$, Lorentzian half-width $\gamma$, at line center position $\lambda_c$, for the $j^{th}$ spectral line.  The amplitude $a$ is always expected to be positive for absorption lines, and is equal to the area under the curve of the line since the Voigt profile is normalized.

The model evaluated with its coarse initial values would have terrible performance: it would only vaguely resemble the synthetic spectral model, with up to $\pm 50\%$ undulations from the inexact assignment of widths,lineshapes, and amplitudes.  Instead, we tune the parameters of the model, starting from these coarse initial values.  This model has $N_{\mathrm{lines}}\times 3$ free parameters, where the center wavelength is held fixed and the amplitude, width, and lineshape are allowed to vary.  We minimize a scalar loss function, which we define as the sum of the squares of the residual vector, $\mathsf{R} \equiv \mathsf{S}-\mathsf{M}$:

\begin{eqnarray}
  \mathcal{L} = \sum_i^{N_s} (S_i - M_i)^2 = \mathsf{R^\intercal}\cdot \mathsf{R}
\end{eqnarray}

As seen in Figure XX, the number of lines can exceed $XX$, meaning the model has over $XX \times 3 = ZZ$ free parameters.  Fitting that large number of parameters is difficult with conventional optimizers, which struggle to converge after hundreds of parameters\authorcomment1{Citation to limits of optimizers}.

Here we employ a variant of Stochastic Gradient Descent, an optimization technique that can scale to a virtually unlimited number of parameters\authorcomment1{provide a citation}.  This technique computes the derivative of the loss scalar with respect to each of the parameters, so for example %\frac{\partial \mathcal{L}}{\partial a}
